Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
DSN changes

\subsection{Conventions}
\begin{itemize}
    \item We assume ordered tuples and strings are indexable via square
        brackets. Occasionally we use subscripts for referring to
        elements of tuples with named members.
    \item We use MD4 as specified in RFC 1320 \cite{rfc1320}.
\end{itemize}

\textbf{TODO}

\subsection{Collisions in Hash Functions}

We use the following terminology when discussing the notion of collisions in
a hash function.

\begin{itemize}
    \item A \textit{cryptographic hash function} is a function:
        \begin{align*}
            h: S_{i} \times B \rightarrow S_{o}
        \end{align*}
        which satisfies the usual properties of cryptographic hash functions
        (preimage, second preimage, collision, deterministic, etc.). We denote
        the input state space as $S_{i}$, the input block space as $B$, and the
        output state space as $S_{o}$. Usually the input state space and the
        output state space are the same, so we omit the subscripts, $S$. We
        assume that these are sets of binary strings of a fixed length. In the
        case of MD4, $S$ is all binary strings of length 128, and $B$ is all
        binary strings of length 512.

    \item An \textit{input} to a hash function is an ordered pair, $i = (s, b)$,
        where $s \in S$ and $b \in B$. The \textit{input space} is simply
        the domain of the hash function, which we denote as $\mathcal{I}$.
        If $i \in \mathcal{I}$ is an input, we reference the state as $i_s$
        and the input block as $i_b$.

    \item We use the term \textit{intermediate state variables} to refer to
        intermediate steps in the computation of a hash function under
        a specific input. Typically these are the outputs of
        one-way compression functions as part of the Merkel-Damg{\aa}rd
        construct. If $i$ is an input to a hash function, we use $I(i)$ to
        denote the intermediate state variables. Formally, this is represented
        as an ordered tuple of binary strings of the size of the updated state.
        In the case of MD4, this is an ordered tuple of cardinality 48, where
        each index is a binary string of length 32, for a total of 1536
        intermediate state variables. We denote the space that $I(i)$ maps
        into as $\mathcal{V}$. We define the number of rounds as $R$.

    \item We use the notation $R(I)$

>>>>

In order to define our define our metrics using logical cryptanalysis
we first define a set of formal terminology and notation whn
discussing our work, and the notation of collisions within a hash. 
We make the general assumption that ordered tuples and strings are
indexable via square brackets. We utilize subscripts when referring to
elements of tuples with named members, as opposed to just indexable
members.  When referring to the MD4 hash function, we use MD4 as
specified in RFC 1320 \cite{rfc1320}.

A \textit{cryptographic hash function} is a function:
\begin{align*}
  h: S_{i} \times B \rightarrow S_{o}
\end{align*}
which satisfies the usual properties of cryptographic hash functions
(preimage, second preimage, collision, deterministic, etc.). We denote
the input state space as $S_{i}$, the input block space as $B$, and the
output state space as $S_{o}$. Usually the input state space and the
output state space are the same, so we omit the subscripts, $S$. We
assume that these are sets of binary strings of a fixed length. In the
case of MD4, $S$ is all binary strings of length 128, and $B$ is all
binary strings of length 512.

An \textit{input} to a hash function is an ordered pair, $i = (s, b)$,
where $s \in S$ and $b \in B$. The \textit{input space} is simply
the domain of the hash function, which we denote as $\mathcal{I}$.
If $i \in \mathcal{I}$ is an input, we reference the state as $i_s$
and the input block as $i_b$.

We use the term \textit{intermediate state variables} to refer to
intermediate steps in the computation of a hash function under
a specific input. Typically these are the outputs of
one-way compression functions as part of the Merkel-Damg{\aa}rd
construct. If $i$ is an input to a hash function, we use $I(i)$ to
denote the intermediate state variables. Formally, this is represented
as an ordered tuple of binary strings of the size of the updated state.
In the case of MD4, this is an ordered tuple of cardinality 48, where
each index is a binary string of length 32, for a total of 1536
intermediate state variables. We denote the space that $I(i)$ maps
into as $\mathcal{V}$. We define a set of functions $R(x)$ where $x$
is an element derived from the sets $\mathcal{C}$ or $\mathcal{F}$
which returns an element.
